\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-26 coq-example.tex
comments in examples section

We construct four families, in one inheritance chain.\YZ{Why is it useful to define these concrete and abstract interpreters as an inheritance chain?}\EDJreply{I don't think these examples are here to show the example themselves are useful. They are here to show family inheritance is useful, and can extend stuff to all sorts of things. I also add some details below on how each family can be extended and what each family means.}

The first family "Lang" define the big step operator (using fuel) of a while language, with expression. But it postulates the computational information of "State" used by Lang. It takes about 200+ LOCs. We can swap the implementation of "State" to have different memory/state management by extending family "Lang".

@@

And at the end, we compile LangRun into module and use Coq to run it on some simple queries. This "LangRun" also illustrates that we still have computability in the presence of family.

>>>>

We construct four families, in one inheritance chain.\YZ{Why is it useful to define these concrete and abstract interpreters as an inheritance chain?}\EDJreply{I don't think these examples are here to show the example themselves are useful. They are here to show family inheritance is useful, and can extend stuff to all sorts of things. I also add some details below on how each family can be extended and what each family means.}\YZreply{Why is it desired to define the abstract interpreter as an extension of the concrete interpreter family? What is lost by putting the two interpreters in the same family?}

The first family "Lang" define the big step operator (using fuel) of a
while language, with expression. But it postulates the computational
information of "State" used by Lang. It takes about 200+ LOCs. We
can\YZ{In general, in a result section like this, you want to show what
you *have done* rather than what you *can do*.}
swap the implementation of "State" to have different memory/state
management by extending family "Lang".\YZ{What is 'different
memory/state management'?}

@@

And at the end, we compile LangRun into module and use Coq to run it on
some simple queries. This "LangRun" also illustrates that we still have
computability in the presence of family.\YZ{Can there be a diagram (a la Figure 1 in Familia paper) illustrating the relationships between (and functionalities of) the different families?}
